Cradles of the first stars: self-shielding, halo masses, and multiplicity

### 2019-09-23 referee.tex
Fixed halo mass for resultion testing.

The 10 pc quoted above is a parameter called StarClusterCombineRadius, and controls how many stars form within a certain spatial range. Within our original simulation, this parameter was set to 10 pc, meaning that all stars younger than 10 kyr and within 10 pc of each other are merged into a single star. To make sure that this value does not affect our results, we have run simulations for a range of this parameter, namely from 0.625 pc to the original 10 pc. The simulations are a 1 comoving Mpc$^3$ box, zoomed-in on a single halo with a mass of $10^{7.7} M_{\odot}$ at the end of the run. \jhw{Double check the mass. Looking at the projections of the halo, its virial radius is about 100 pc, which corresponds to a halo mass around $10^6 M_\odot$.} The simulations run for a total of 10 Myr. We see the same number of Pop III stars form regardless of the chosen value for the merging parameter. Thus, our results are independent of this value. This detail has been added to section 2.2.1.

@@

@@

@@

>>>>

The 10 pc quoted above is a parameter called StarClusterCombineRadius, and controls how many stars form within a certain spatial range. Within our original simulation, this parameter was set to 10 pc, meaning that all stars younger than 10 kyr and within 10 pc of each other are merged into a single star. To make sure that this value does not affect our results, we have run simulations for a range of this parameter, namely from 0.625 pc to the original 10 pc. The simulations are a 1 comoving Mpc$^3$ box, zoomed-in on a single halo with a mass of $10^{5.8} M_{\odot}$ at the end of the run. The simulations run for a total of 10 Myr. We see the same number of Pop III stars form regardless of the chosen value for the merging parameter. Thus, our results are independent of this value. This detail has been added to section 2.2.1.

@@

\jhw{Readdress this point, using that $\rho_c = \rho_m$ at high redshifts.}

@@

\jhw{I can answer this point.}

@@

\jhw{We are still investigating this issue. Calculate the matter power spectrum and compare with the analytic expectation to see if the simulation was initialized with some odd mode.}
